Formal verification of train route planning

### 2025-06-28 paper/main.tex
Add 3steps experiments

@@

Our third contribution is a composition operator. This operator allows to incrementally build routing schedules, which can then be tested using our TLA+ implementation. Our composition distinguishes safe steps: steps where no two trains use the same track. Our composition can append safe steps to arbitrary schedules, creating new schedules. We implemented our composition operator in Python and we tested it by model checking all schedules composed of two and three safe steps in our small-scale network. The computation time was found to be affordable for companies: checking all two-steps schedules took less than an hour on a cluster, using 8 nodes of 18 cores.
Our implementation, including both the TLA model and the Python composition is available on \url{https://doi.org/10.5281/zenodo.15761521}.\todo{Remplacer Zenodo si on a le temps}.

>>>>

We also tested about 10000 composition of three safe steps, which all succeeded\footnote{10.791 compositions were tested on the cluster, 91 failed. We suspect the failures are due to the cluster environment. The 91 cases turned out to be correct after double checking on a personal computer.}.

@@

Our third contribution is a composition operator. This operator allows to incrementally build routing schedules, which can then be tested using our TLA+ implementation. Our composition distinguishes safe steps: steps where no two trains use the same track. Our composition can append safe steps to arbitrary schedules, creating new schedules. We implemented our composition operator in Python and we tested it by model checking all schedules composed of two and three safe steps in our small-scale network. The computation time was found to be affordable for companies: checking all two-steps schedules took less than an hour on a cluster, using 8 nodes of 18 cores.
Our implementation, including both the TLA model and the Python composition is available on \url{https://doi.org/10.5281/zenodo.15761521}.
